---
output: bd::html_body
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("vitae-md.R")
```

# Brecht Devleesschauwer

Assistant Scientist, Global Food Safety and Zoonoses, PhD DVM MVSc MStat

_Emerging Pathogens Institute & Department of Animal Sciences, University of Florida_  
_Center for Burden and Risk Assessment_---[www.cbra.be](http://www.cbra.be})

bdevleesschauwer@ufl.edu | [animal.ifas.ufl.edu/faculty/devleesschauwer](http://animal.ifas.ufl.edu/faculty/devleesschauwer) | +1 352 392 1981  
2250 Shealy Drive, Gainesville, FL 32611, USA | PO Box 110910

## Research interests

* Epidemiology, burden of disease, risk assessment, health economics;
* Bayesian data analysis, true prevalence estimation, meta-analysis, disease mapping;
* Zoonotic diseases, food safety, veterinary public health.

## Employment

* **Assistant scientist**, 06/2015--present  
    University of Florida, Gainesville, USA  
    Activities: 90% research, 10% teaching
    
* **Post-doctoral researcher**, 04/2015  
    Ghent University, Merelbeke, Belgium
    
* **Contracted technical expert**, 09/2013--12/2013, 02/2014--03/2014  
    World Health Organization, Geneva, Switzerland
    
* **Doctoral researcher**, 10/2010--03/2015  
    Ghent University, Merelbeke, Belgium  
    Université catholique de Louvain, Brussels, Belgium

## Education

### Academic titles

* **Ph.D. Veterinary Sciences & Ph.D. Public Health**, 2010--2015  
    Ghent University, Merelbeke, Belgium  
    Université catholique de Louvain, Brussels, Belgium  
    Dissertation topic: _The Burden of Zoonoses in Nepal_  
    Promoters: Prof. Dr. P. Dorny, Prof. Dr. N. Speybroeck, Prof. Dr. L. Duchateau

* **Doctoral Training Programme**, 2010--2015  
    Doctoral School of Life Sciences and Medicine, Ghent University, Belgium

* **M.Sc. Statistics (biometrics)**, 2011--2014  
    Katholieke Universiteit Leuven, Louvain, Belgium; Great distinction  
    Dissertation topic: _Quantitative Microbial Risk Assessment with R_  
    Promoters: Prof. Dr. G. Molenberghs, Prof. Dr. C. Faes

* **M.Sc. Veterinary Medicine (research & industry)**, 2007--2010  
    Ghent University, Merelbeke, Belgium; Greatest distinction  
    Dissertation topic: _The Epidemiology of Taenia solium in Nepal_  
    Promoter: Prof. Dr. P. Dorny

* **B.Sc. Veterinary Medicine**, 2004--2007  
    Ghent University, Merelbeke, Belgium; Greatest distinction

### Short courses

## Scientific output

### Peer-reviewed papers

**[Google Scholar](https://scholar.google.com/citations?user=AFSxtd0AAAAJ) metrics: `r gs$total_cites` citations &middot; h-index `r gs$h_index` &middot; i10-index `r gs$i10_index`**

```{r, echo=FALSE, results='asis', message=FALSE}
wb <- loadWorkbook("publications.xlsx")
setMissingValue(wb, value = "NA")

db <- readWorksheet(wb, sheet = "published")
db <- db[order(db$title), ]
db <- db[order(db$date, decreasing = TRUE), ]
db <- db[order(!is.na(db$volume)), ]
for (i in seq(nrow(db))) print_article(db[i, ], nrow(db) - i + 1)
```

---

_Last update: `r Sys.Date()`_