---
output: bd::html_body
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("vitae-md.R")
```

# Brecht Devleesschauwer

Senior epidemiologist, PhD DVM MVSc MStat

_Scientific Institute of Public Health (WIV-ISP), Department of Public Health and Surveillance_  
_Center for Burden and Risk Assessment_---[www.cbra.be](http://www.cbra.be)

brecht.devleesschauwer@wiv-isp.be | Skype: <a href="skype:brecht.devleesschauwer?call">brecht.devleesschauwer</a>  
Rue Juliette Wytsmanstraat 14, 1050 Brussels, Belgium | +32 2 642 5035

## Research interests

* Epidemiology, burden of disease, risk assessment, health economics;
* Bayesian data analysis, true prevalence estimation, disease transmission modeling;
* Zoonotic diseases, food safety, veterinary public health.

## Employment

* **Senior epidemiologist, coordinator national burden of disease studies**, 04/2016--present  
    Scientific Institute of Public Health (WIV-ISP), Brussels, Belgium

* **Guest lecturer, health economic evaluations**, 10/2016--present  
    Université catholique de Louvain, Brussels, Belgium
    
* **Assistant scientist, global food safety and zoonoses**, 06/2015--03/2016  
    University of Florida, Gainesville, FL, USA
    
* **Post-doctoral researcher**, 04/2015  
    Ghent University, Merelbeke, Belgium
    
* **Contracted technical expert**, 09/2013--12/2013, 02/2014--03/2014  
    World Health Organization, Geneva, Switzerland
    
* **Doctoral researcher**, 10/2010--03/2015  
    Ghent University, Merelbeke, Belgium  
    Université catholique de Louvain, Brussels, Belgium

## Education

### Academic titles

* **Ph.D. Veterinary Sciences & Ph.D. Public Health**, 2010--2015  
    Ghent University, Merelbeke, Belgium  
    Université catholique de Louvain, Brussels, Belgium  
    Dissertation topic: _The Burden of Zoonoses in Nepal_  
    Promoters: Prof. Dr. P. Dorny, Prof. Dr. N. Speybroeck, Prof. Dr. L. Duchateau

* **Doctoral Training Programme**, 2010--2015  
    Doctoral School of Life Sciences and Medicine, Ghent University, Belgium

* **M.Sc. Statistics (biometrics)**, 2011--2014  
    Katholieke Universiteit Leuven, Louvain, Belgium; Great distinction  
    Dissertation topic: _Quantitative Microbial Risk Assessment with R_  
    Promoters: Prof. Dr. G. Molenberghs, Prof. Dr. C. Faes

* **M.Sc. Veterinary Medicine (research & industry)**, 2007--2010  
    Ghent University, Merelbeke, Belgium; Greatest distinction  
    Dissertation topic: _The Epidemiology of Taenia solium in Nepal_  
    Promoter: Prof. Dr. P. Dorny

* **B.Sc. Veterinary Medicine**, 2004--2007  
    Ghent University, Merelbeke, Belgium; Greatest distinction

### Short courses

```{r, echo=FALSE, results='asis', message=FALSE}
db <- readWorksheetFromFile("short_courses.xlsx", "index")
db <- db[order(db$title), ]
db <- db[order(db$year, decreasing = TRUE), ]

for (i in seq(nrow(db))) {
  cat("* **", db$title[i], "**, ", db$year[i], "  \n", sep = "")
  cat("    ", db$location[i], "\n\n")
}
```

## Professional experiences

### Contributions to peer review

* **Academic Editor, 2017**--present  
    PLOS ONE

* **Associate Editor, 2017**--present  
    BMC Veterinary Research, Parasitology section

* **Reviewer for international scientific journals**, e.g.:  
```{r, echo=FALSE, results='asis', message=FALSE}
journals <-
  read.table("journals.txt", stringsAsFactors = FALSE, sep = "\t")$V1
cat(sanitize_specials(paste(sort(journals), collapse = ", "), "html"))
```

### Participation in international projects

* **Country representative**, 2016--present   
    European Burden of Disease Network (WHO/EURO, IHME)
    
* **Epidemiology workgroup leader**, 2013--present   
    EU COST action TD1302 CYSTINET---[www.cystinet.org](http://www.cystinet.org)

* **Risk forecasting workgroup vice-leader**, 2015--2016   
    EU COST action FA1408 EURO-FBP
    
* **USAID Feed the Future Innovation Lab on Livestock Systems**, 2015--2016  
    _Project granted to UF, aiming to improve livestock systems in Mali, Burkina Faso, Ethiopia, Rwanda, Nepal and Cambodia_
    * Contribution to project proposal
    * Participation in Livestock Disease Management and Food Safety AOI  

* **Computational Task Force member**, 2011--2015  
    **Country Studies Task Force member**, 2011--2015  
    [Foodborne Disease Burden Epidemiology Reference Group](http://www.who.int/foodsafety/areas_work/foodborne-diseases/ferg/en/), WHO  
    
* **VLIR-UOS Institutional University Cooperation with Jimma University, Ethiopia**, 2012--2015 
    _Collaboration between Jimma University and different Flemish universities to strenghten institutional capacity_
    * Organisation of a workshop on design of experiments
    * Supervision of Master students   
    
* **Doctoral research in Nepal**, 2010--2015  
    _Collection and analysis of data on the burden of zoonotic and foodborne diseases, during a 6 months' stay_  
    
* **Impact assessment and control of cysticercosis in the Indian Subcontinent**, 2007--2009  
    _VLIR-UOS collaboration between Institute of Tropical Medicine (Antwerp, Belgium) and National Zoonoses and Food Hygiene Research Centre (Kathmandu, Nepal)_
    * Field work, lab work, data analysis

### Contributions as invited expert

* FAO/WHO expert meeting on verotoxigenic _Escherichia coli_ (VTEC) / Shigatoxigenic _E. coli_ (STEC). World Health Organization, Geneva, Switzerland; 2016.

* Expert consultation on diet-related health problems to support the development of food-based dietary guidelines. Superior Health Council, Brussels, Belgium; 2016.

* Expert panel on FDA-iRisk DALY templates. Research Triangle International, NC, USA; 2016.

* Expert consultation to discuss preliminary results of the joint WHO/IHME analysis of causes of death among children aged 5--14 years in the WHO European Region. WHO Regional Office for Europe, Copenhagen, Denmark; 2015.

* Trend analysis applied to parameter/matrix combinations from the the control plan. Federal Agency for the Safety of the Food Chain, Brussels, Belgium; 2014.

* FAO/WHO Expert Meeting on Risk-based examples for Control of _Trichinella_ spp. and _Taenia saginata_ in meat. World Health Organization, Geneva, Switzerland; 2013--2014.

### Logistic responsibilities

#### Management of research centers

* **Founding member**, 2014--present  
    Center for Burden and Risk Assessment, [www.cbra.be](http://www.cbra.be)

#### Organisation of national and international conferences

* **Member of scientific committee**  
    1st International CYSTINET Conference, 3--4 November 2015, Belgrade, Serbia

#### Other

* **Event organizer**, 2012--2014  
    RBelgium, the Belgian R user group
    
* **Rapporteur**, November 2010  
    Fourth meeting of the Foodborne Disease Burden Epidemiology Reference Group  
    WHO Headquarters, Geneva, Switzerland

## Skills

### Languages

Language | Speaking | Reading | Writing
-------- | -------- | ------- | -------
Dutch    | +++      | +++     | +++
English  | +++      | +++     | +++
French   | ++       | +++     | ++
German   | +        | ++      | + 
Nepali   | +        | +       | + 

### Computer skills

* **Statistical software**: R, WinBUGS, OpenBUGS, JAGS, SAS, Stata
* **Advanced R skills**: package development, Tcl/Tk interfaces, Shiny applications
* **Design and programming**: html, javascript, php, mysql, LaTeX, markdown, C++
* **Windows and MS Office**: Word, Excel, Powerpoint, Access

## Teaching

### Courses

* **Health economic evaluations**  
    WFSP2103, Université catholique de Louvain, March--April 2017  

* **Quantitative microbial risk assessment of pathogens in food systems**  
    ANS 6932 / FOS 6936, University of Florida, February 26--March 4 2016  

### Workshops

* **Burden of Disease and the DALY metric**, 5--6 October 2016   
    WIV-ISP, Brussels, Belgium
    
* **CYSTINET Epidemiology Training School**, 1--3 September 2014   
    Institute of Tropical Medicine, Antwerp, Belgium   
    Contents: introduction to R, systematic review and meta-analysis, GIS
    
* **National Workshop on Design of Experiments for Statisticians and Practitioners**, 28--29 March 2013   
    Jimma University, Jimma, Ethiopia   
    Partims: introduction to R, analysis of variance

### Lectures

* **Topics in tropical veterinary medicine**, 2013--2016  
    MSc Veterinary Medicine, Ghent University
    
* **Food safety: an introduction**, 2015   
    Environmental Health Concepts in Public Health, PHC 6313, University of Florida
    
* **Concepts of health economics**, 2013--2014   
    MSc Public Health, Université catholique de Louvain
    
* **Burden of disease and the Disability-Adjusted Life Year**, 2013--2015   
    MSc Public Health, Université catholique de Louvain   
    MSc Health and Development, Université catholique de Louvain   
    MSc Occupational Medicine, Université catholique de Louvain   
    BSc Biomedical Sciences, Université catholique de Louvain
    
* **Diagnostic test characteristics and true prevalence**, 2013--2014   
    MSc Public Health, Université catholique de Louvain   
    MSc Health and Development, Université catholique de Louvain

### Practicals

* **Biomedical statistics**, 2012--2014   
    BSc Veterinary Medicine, Ghent University
    
* **Applied biomedical statistics**, 2013--2014   
    MSc Veterinary Medicine, Ghent University


### Promoter of 4 short-term scientific missions

* **Fabian Dupont**, October 2015   
    MSc Medicine, Technische Universität München   
    Health and economic impact of _Taenia solium_ neurocysticercosis in Uganda
    
* **Uffe Christian Braae**, December 2014   
    PhD Veterinary Medicine, University of Copenhagen   
    Development of a _Taenia solium_ transmission model
    
* **Dr Hardy Richter**, September 2014   
    Research associate, Munich Global Neurology Group   
    Landscape analysis of _Taenia solium_ neurocysticercosis in Europe
    
* **Chiara Trevisan**, July 2014   
    PhD Veterinary Medicine, University of Copenhagen   
    Burden assessment of _Taenia solium_ cysticercosis in Tanzania


```{r, echo=FALSE, results='asis', message=FALSE}
wb <- loadWorkbook("students.xlsx")
setMissingValue(wb, value = "NA")
db <- readWorksheet(wb, sheet = "students")

db_msc <- db[db$grade == "MSc", ]
db_msc <- db_msc[order(db_msc$year, decreasing = TRUE), ]
cat(sprintf("### (Co)supervisor of %d MSc students\n", nrow(db_msc)))

for (i in seq(nrow(db_msc)))
  print_student(db_msc[i, ], nrow(db_msc) - i + 1)

db_bsc <- db[db$grade == "BSc", ]
db_bsc <- db_bsc[order(db_bsc$year, decreasing = TRUE), ]
cat(sprintf("### (Co)supervisor of %d BSc students\n", nrow(db_bsc)))

for (i in seq(nrow(db_bsc)))
  print_student(db_bsc[i, ], nrow(db_bsc) - i + 1)
```

## Scientific output

```{r, echo=FALSE, message=FALSE}
wb <- loadWorkbook("publications.xlsx")
setMissingValue(wb, value = "NA")

db <- readWorksheet(wb, sheet = "chapters")
db <- db[order(db$title), ]
db <- db[order(db$date, decreasing = TRUE), ]
```

```{r, echo=FALSE, results='asis'}
cat(sprintf("### Book chapters (%d)", nrow(db)))
```

```{r, echo=FALSE, results='asis', message=FALSE}
for (i in seq(nrow(db))) print_chapter(db[i, ], nrow(db) - i + 1)
```

```{r, echo=FALSE, message=FALSE}
wb <- loadWorkbook("publications.xlsx")
setMissingValue(wb, value = "NA")

db <- readWorksheet(wb, sheet = "papers")
db <- db[order(db$title), ]
db <- db[order(db$date, decreasing = TRUE), ]
db <- db[order(!is.na(db$volume)), ]
```

```{r, echo=FALSE, results='asis'}
cat(sprintf("### Peer-reviewed papers (%d)", nrow(db)))
```

**[Google Scholar](https://scholar.google.com/citations?user=AFSxtd0AAAAJ) metrics: `r gs$total_cites` citations &middot; h-index `r gs$h_index` &middot; i10-index `r gs$i10_index`**

```{r, echo=FALSE, results='asis', message=FALSE}
for (i in seq(nrow(db))) print_article(db[i, ], nrow(db) - i + 1)
```

```{r, echo=FALSE, message=FALSE}
db <- readWorksheet(wb, sheet = "submitted")
db <- db[order(db$title), ]
db <- db[order(db$date, decreasing = TRUE), ]
```

```{r, echo=FALSE, results='asis'}
cat(sprintf("### Submitted manuscripts (%d)", nrow(db)))
```

```{r, echo=FALSE, results='asis', message=FALSE}
for (i in seq(nrow(db))) print_article(db[i, ], nrow(db) - i + 1)
```

```{r, echo=FALSE, message=FALSE}
wb <- loadWorkbook("presentations.xlsx")
setMissingValue(wb, value = "NA")

db <- readWorksheet(wb, sheet = "oral")
db <- db[order(db$title), ]
db <- db[order(db$month, decreasing = TRUE), ]
db <- db[order(db$year, decreasing = TRUE), ]
```

```{r, echo=FALSE, results='asis'}
cat(sprintf("### Oral presentations (%d)", nrow(db)))
```

```{r, echo=FALSE, results='asis', message=FALSE}
for (i in seq(nrow(db))) print_proceeding(db[i, ], nrow(db) - i + 1)
```

```{r, echo=FALSE, message=FALSE}
db <- readWorksheet(wb, sheet = "poster")
db <- db[order(db$title), ]
db <- db[order(db$month, decreasing = TRUE), ]
db <- db[order(db$year, decreasing = TRUE), ]
```

```{r, echo=FALSE, results='asis'}
cat(sprintf("### Poster presentations (%d)", nrow(db)))
```

```{r, echo=FALSE, results='asis', message=FALSE}
for (i in seq(nrow(db))) print_proceeding(db[i, ], nrow(db) - i + 1)
```

### Reports

* Graham H, Martijn Bouwknegt M, **Devleesschauwer B**, Robertson L, van der Giessen L (2016) COST Action FA1408: European ranking of foodborne parasites. Results of a workshop held to prioritise foodborne parasites in Europe using multicriteria decision analyses, 8--12 February 2016, RIVM Bilthoven.

* World Health Organization (2015) WHO estimates of the global burden of foodborne diseases. Foodborne diseases burden epidemiology reference group 2007--2015. Geneva: WHO Press. http://www.who.int/foodsafety/publications/foodborne_disease/fergreport/en/

* Smit S, **Devleesschauwer B**, Apers L, Macq J, Beutels P, Speybroeck N (2015) Evaluation of the cost-effectiveness of the tuberculosis policies in Flanders. Report submitted to the Agency for Care and Health.

* Food and Agriculture Organization of the United Nations, World Health Organization (2014) Risk based examples for control of _Trichinella_ spp. and _Taenia saginata_ in meat. Report of a joint FAO/WHO expert meeting, 22--25 October 2013, WHO Headquarters, Geneva, Switzerland. ftp://ftp.fao.org/codex/meetings/CCFH/ccfh46/Trichinella%20Mtg%20Report%20241014.pdf

* World Health Organization (2014) WHO initiative to estimate the global burden of foodborne diseases: fifth formal meeting of the Foodborne Disease Burden Epidemiology Reference Group (FERG), 8--12 April 2013, Geneva, Switzerland. Geneva: WHO Press. http://www.who.int/foodsafety/publications/ferg5/en/

* World Health Organization (2014) WHO initiative to estimate the global burden of foodborne diseases: fourth formal meeting of the Foodborne Disease Burden Epidemiology Reference Group (FERG): Sharing New Results, Making Future Plans, and Preparing Ground for the Countries. Geneva: WHO Press. http://www.who.int/foodsafety/publications/ferg4/en/

### R Packages

```{r, echo=FALSE, message=FALSE, results='asis'}
db <- readWorksheetFromFile("Rpackages.xlsx", sheet = "tab")
db <- db[order(db$date, decreasing = TRUE), ]
for (i in seq(nrow(db))) {
  print_package(db[i, ], nrow(db) - i + 1)
}
```

### Vulgarizing articles

* Havelaar AH, **Devleesschauwer B**. _One in 10 globally suffer from foodborne diseases, WHO study finds._ EPI News, 3 December 2015.
* Speybroeck N, Maertens de Noordhout C, **Devleesschauwer B**. _Des nombres pour des aliments sûrs._ La Libre Belgique, 12 April 2015.
* Speybroeck N, Maertens de Noordhout C, **Devleesschauwer B**. _Comment les nombres rendent vos aliments plus sûrs._ Le Soir, 8 April 2015.
* Speybroeck N, Maertens de Noordhout C, **Devleesschauwer B**. _Hoe getallen je voedsel veiliger maken._ De Morgen, 7 April 2015.

## Scientific honors and awards

* **PhD Scholarship**, Special Research Fund (BOF), Ghent University; 2010
* **Pfizer Award** for the best Master thesis in Veterinary Medicine; 2010
* **Dr Paul Janssen Award** for the best Master student in Veterinary Medicine; 2010
* **Floribert Jurion Fund**, Royal Academy for Overseas Sciences; 2009
* **Travel grant**, BIOS, Ghent University; 2008
* **Travel grant**, Flemish Inter-University Council---University Development Cooperation (VLIR-UOS); 2007

---

_Last update: `r Sys.Date()`_