---
output: bd::html_body
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("vitae-md.R")
```

# Brecht Devleesschauwer

Senior epidemiologist, PhD DVM MVSc MStat

_Sciensano, Department of Epidemiology and Public Health_  
_Center for Burden and Risk Assessment_---[www.cbra.be](http://www.cbra.be)

brecht.devleesschauwer@sciensano.be | Skype: <a href="skype:brecht.devleesschauwer?call">brecht.devleesschauwer</a>  
Rue Juliette Wytsman 14, 1050 Brussels, Belgium | +32 2 642 5035

## Research interests

* Epidemiology, burden of disease, health impact assessment, risk assessment;
* Bayesian data analysis, true prevalence estimation, disease transmission modeling;
* Zoonotic diseases, food safety, veterinary public health.

## Employment

* **Visiting professor, risk analysis**, 04/2018--present  
    Ghent University, Merelbeke, Belgium

* **Senior epidemiologist, coordinator national burden of disease studies**, 04/2016--present  
    Sciensano, Brussels, Belgium

* **Visiting professor, advanced epidemiology**, 10/2018--09/2019  
    Université catholique de Louvain, Brussels, Belgium

* **Visiting professor, health economic evaluations**, 10/2016--09/2018  
    Université catholique de Louvain, Brussels, Belgium
    
* **Assistant scientist, global food safety and zoonoses**, 06/2015--03/2016  
    University of Florida, Gainesville, FL, USA
    
* **Post-doctoral researcher**, 04/2015  
    Ghent University, Merelbeke, Belgium
    
* **Contracted technical expert**, 09/2013--12/2013, 02/2014--03/2014  
    World Health Organization, Geneva, Switzerland
    
* **Doctoral researcher**, 10/2010--03/2015  
    Ghent University, Merelbeke, Belgium  
    Université catholique de Louvain, Brussels, Belgium

## Education

### Academic titles

* **Ph.D. Veterinary Sciences & Ph.D. Public Health**, 2010--2015  
    Ghent University, Merelbeke, Belgium  
    Université catholique de Louvain, Brussels, Belgium  
    Dissertation topic: _The Burden of Zoonoses in Nepal_  
    Promoters: Prof. Dr. P. Dorny, Prof. Dr. N. Speybroeck, Prof. Dr. L. Duchateau

* **Doctoral Training Programme**, 2010--2015  
    Doctoral School of Life Sciences and Medicine, Ghent University, Belgium

* **M.Sc. Statistics (biometrics)**, 2011--2014  
    Katholieke Universiteit Leuven, Louvain, Belgium; Great distinction  
    Dissertation topic: _Quantitative Microbial Risk Assessment with R_  
    Promoters: Prof. Dr. G. Molenberghs, Prof. Dr. C. Faes

* **M.Sc. Veterinary Medicine (research & industry)**, 2007--2010  
    Ghent University, Merelbeke, Belgium; Greatest distinction  
    Dissertation topic: _The Epidemiology of Taenia solium in Nepal_  
    Promoter: Prof. Dr. P. Dorny

* **B.Sc. Veterinary Medicine**, 2004--2007  
    Ghent University, Merelbeke, Belgium; Greatest distinction

### Short courses

```{r, echo=FALSE, results='asis', message=FALSE}
db <- read_excel("short_courses.xlsx", "index")
db <- db[order(db$title), ]
db <- db[order(db$year, decreasing = TRUE), ]

for (i in seq(nrow(db))) {
  cat("* **", db$title[i], "**, ", db$location[i], ", ", db$year[i], "  \n\n", sep = "")
}
```

## Professional experiences

### Contributions to peer review
    
* **Academic/Associate Editor**  
    PLOS ONE (2017--present)  
    Food and Waterborne Parasitology (2017--present)  
    BMC Veterinary Research, Parasitology section (2017--2019)

* **Guest Editor**  
    Archives of Public Health: [burden of disease article collection](https://www.biomedcentral.com/collections/burden-of-disease) (2019--present)

* **Reviewer for international scientific journals**, e.g.:  
```{r, echo=FALSE, results='asis', message=FALSE}
journals <-
  read.table("journals.txt", stringsAsFactors = FALSE, sep = "\t")$V1
cat(sanitize_specials(paste(sort(journals), collapse = ", "), "html"))
```

### Participation in national projects

* **Principal investigator**, 2020--2025   
    HELICON --  Unravelling the long-term and indirect health impact of the coronavirus crisis in Belgium---[www.brain-helicon.be](https://www.brain-helicon.be)

* **Principal investigator**, 2020--2023   
    AHEAD -- Towards the development of a national health data platform

* **Principal investigator**, 2019--2024   
    ELLIS -- Monitoring and mitigating environmental health inequalities in Belgium---[www.brain-ellis.be](https://www.brain-ellis.be)

* **Principal investigator**, 2019--2023   
    WaIST --  Contribution of excessive weight status to the social impact of non-communicable diseases, multimorbidity and disability in Belgium: past, present, and future
        
* **Project manager**, 2018--2019   
    Diagnosis-based morbidity statistics -- Pilot data collection
    
* **Project co-manager**, 2017--present   
    Belgian Health Status Report

* **Project manager**, 2016--present   
    Belgian National Burden of Disease Study

* **Project manager**, 2016--present   
    Belgian contribution to the WHO/EURO Health for All Database

* **Project collaborator**, 2016--present   
    Belgian Health System Performance Assessment

### Participation in international projects

* **WP member**, 2021--present   
    WP4 Data analysis, Unravelling Data for Rapid Evidence-Based Response to COVID-19---[www.uncover-eu.net](https://www.uncover-eu.net)

* **WP member**, 2021--present   
    WP5 Research methodologies to assess the impact of COVID-19, The Population Health Information Research Infrastructure---[www.phiri.eu](https://www.phiri.eu)

* **Human Health Theme co-lead**, 2021--present   
    Global Burden of Animal Diseases programme---[www.animalhealthmetrics.org](https://www.animalhealthmetrics.org)

* **Main Action Proposer and Chair**, 2019--present   
    COST Action CA18218 European Burden of Disease Network---[www.burden-eu.net](https://www.burden-eu.net)

* **Country representative**, 2017--present   
    EUROSTAT Technical Group on Morbidity Statistics

* **Country representative**, 2016--present   
    European Burden of Disease Network (WHO/EURO, IHME)

* **Epidemiology workgroup leader**, 2013--2018   
    COST Action TD1302 CYSTINET---[www.cystinet.org](http://www.cystinet.org)

* **Risk forecasting workgroup vice-leader**, 2015--2016   
    COST Action FA1408 EURO-FBP
    
* **USAID Feed the Future Innovation Lab on Livestock Systems**, 2015--2016  
    _Project granted to UF, aiming to improve livestock systems in Mali, Burkina Faso, Ethiopia, Rwanda, Nepal and Cambodia_  
    * Contribution to project proposal  
    * Participation in Livestock Disease Management and Food Safety AOI  

* **Computational Task Force member**, 2011--2015  
    **Country Studies Task Force member**, 2011--2015  
    [Foodborne Disease Burden Epidemiology Reference Group](http://www.who.int/foodsafety/areas_work/foodborne-diseases/ferg/en/), WHO  
    
* **VLIR-UOS Institutional University Cooperation with Jimma University, Ethiopia**, 2012--2015 
    _Collaboration between Jimma University and different Flemish universities to strenghten institutional capacity_
    * Organisation of a workshop on design of experiments
    * Supervision of Master students   
    
* **Doctoral research in Nepal**, 2010--2015  
    _Collection and analysis of data on the burden of zoonotic and foodborne diseases, during a 6 months' stay_  
    
* **Impact assessment and control of cysticercosis in the Indian Subcontinent**, 2007--2009  
    _VLIR-UOS collaboration between Institute of Tropical Medicine (Antwerp, Belgium) and National Zoonoses and Food Hygiene Research Centre (Kathmandu, Nepal)_
    * Field work, lab work, data analysis

### Contributions as invited expert

* EFSA working group on foodborne parasites. European Food Safety Authority, Parma, Italy; 2017--2018.

* Steering committee of KCE project 292, [Exploratory steps for the formulation of Belgian health system targets](https://www.kce.fgov.be/en/exploratory-steps-for-the-formulation-of-belgian-health-system-targets). Belgian Health Care Knowledge Centre, Brussels, Belgium; 2017.

* FAO/WHO expert meeting on verotoxigenic _Escherichia coli_ (VTEC) / Shigatoxigenic _E. coli_ (STEC). World Health Organization, Geneva, Switzerland; 2016--2017.

* Expert consultation on diet-related health problems to support the development of food-based dietary guidelines. Superior Health Council, Brussels, Belgium; 2016--2017.

* Expert panel on FDA-iRisk DALY templates. Research Triangle International, NC, USA; 2016.

* Expert consultation to discuss preliminary results of the joint WHO/IHME analysis of causes of death among children aged 5--14 years in the WHO European Region. WHO Regional Office for Europe, Copenhagen, Denmark; 2015.

* Trend analysis applied to parameter/matrix combinations from the the control plan. Federal Agency for the Safety of the Food Chain, Brussels, Belgium; 2014.

* FAO/WHO Expert Meeting on Risk-based examples for Control of _Trichinella_ spp. and _Taenia saginata_ in meat. World Health Organization, Geneva, Switzerland; 2013--2014.

### Logistic responsibilities

#### Institutional responsibilities

* **Workgroup leader**, 2017--present  
    Sciensano Translational Research Working Group
    
* **Member**, 2017--present  
    Sciensano Redactional Council

#### Management of research centers

* **Founding member**, 2014--present  
    Center for Burden and Risk Assessment, [www.cbra.be](http://www.cbra.be)

#### Organisation of national and international conferences

* **Member of scientific committee**  
    1st International CYSTINET Conference, 3--4 November 2015, Belgrade, Serbia

#### Other

* **Event organizer**, 2012--2014  
    RBelgium, the Belgian R user group
    
* **Rapporteur**, November 2010  
    Fourth meeting of the Foodborne Disease Burden Epidemiology Reference Group  
    WHO Headquarters, Geneva, Switzerland

## Skills

### Languages

Language | Speaking | Reading | Writing
-------- | -------- | ------- | -------
Dutch    | +++      | +++     | +++
English  | +++      | +++     | +++
French   | ++       | +++     | ++
German   | +        | ++      | + 
Nepali   | +        | +       | + 

### Computer skills

* **Statistical software**: R, JAGS, WinBUGS, OpenBUGS, SAS, Stata
* **Advanced R skills**: package development, Tcl/Tk interfaces, Shiny applications
* **Design and programming**: html, javascript, php, mysql, LaTeX, markdown, C++
* **Windows and MS Office**: Word, Excel, Powerpoint, Access

## Teaching

### Courses

* **Advanced epidemiology**  
    WFSP2238, Université catholique de Louvain, 2018--2019
    
* **Health economic evaluations**  
    WFSP2103, Université catholique de Louvain, 2016--2018

* **Quantitative microbial risk assessment of pathogens in food systems**  
    ANS 6932 / FOS 6936, University of Florida, February 26--March 4 2016  

### Workshops

* **Burden of Disease and the DALY metric, 2nd edition**, 11--12 October 2017   
    WIV-ISP, Brussels, Belgium
    
* **Burden of Disease and the DALY metric, 1st edition**, 5--6 October 2016   
    WIV-ISP, Brussels, Belgium
    
* **CYSTINET Epidemiology Training School**, 1--3 September 2014   
    Institute of Tropical Medicine, Antwerp, Belgium   
    Contents: introduction to R, systematic review and meta-analysis, GIS
    
* **National Workshop on Design of Experiments for Statisticians and Practitioners**, 28--29 March 2013   
    Jimma University, Jimma, Ethiopia   
    Partims: introduction to R, analysis of variance

### Lectures

* **Risk analysis: concepts and metrics**, 2017--present  
    MSc Veterinary Medicine, Ghent University
    
* **Topics in tropical veterinary medicine**, 2013--2016  
    MSc Veterinary Medicine, Ghent University
    
* **Food safety: an introduction**, 2015   
    Environmental Health Concepts in Public Health, PHC 6313, University of Florida
    
* **Concepts of health economics**, 2013--2014   
    MSc Public Health, Université catholique de Louvain
    
* **Burden of disease and the Disability-Adjusted Life Year**, 2013--2015   
    MSc Public Health, Université catholique de Louvain   
    MSc Health and Development, Université catholique de Louvain   
    MSc Occupational Medicine, Université catholique de Louvain   
    BSc Biomedical Sciences, Université catholique de Louvain
    
* **Diagnostic test characteristics and true prevalence**, 2013--2014   
    MSc Public Health, Université catholique de Louvain   
    MSc Health and Development, Université catholique de Louvain

### Practicals

* **Biomedical statistics**, 2012--2014   
    BSc Veterinary Medicine, Ghent University
    
* **Applied biomedical statistics**, 2013--2014   
    MSc Veterinary Medicine, Ghent University

### PhD students (6)

* **Martina Otavova**, 2020--2024   
    PhD Social Sciences (Demography), Université catholique de Louvain  
    Development and application of a Belgian Index of Multiple Deprivation  
    Promoters: Bruno Masquelier, **Brecht Devleesschauwer**  
    
* **Vanessa Gorasso**, 2020--2024   
    PhD Public Health, Ghent University  
    Health impact assesssment of excess weight status prevention policies  
    Promoters: Delphine De Smedt, **Brecht Devleesschauwer**  
    
* **Margot Cooreman-Algoed**, 2018--2024   
    PhD Bioscience Engineering, Ghent University  
    Integrating environmental and nutritional aspects of diets  
    Promoters: Jo Dewulf, **Brecht Devleesschauwer**  
    
* **Lisa Van Wilder**, 2018--2022   
    PhD Public Health, Ghent University  
    Quality of life in patients with chronic disease  
    Promoters: Delphine De Smedt, Els Clays, **Brecht Devleesschauwer**  

* **Frederik Engelen**, 2018--2021  
    PhD Veterinary Sciences, Ghent University  
    Shiga toxin-producing Escherichia coli: A dangerous gut feeling
    Promoters: Eric Cox, Lieven De Zutter, Jacques Mainil, **Brecht Devleesschauwer**  
    
* **Sofie Theresa Thomsen**, 2016--2019   
    PhD Nutrition, National Food Institute, Danish Technical University  
    Risk-benefit assessment of food substitutions  
    Promoters: Rikke Andersen, Sara Monteiro Pires, Morten Poulsen, **Brecht Devleesschauwer**  

```{r, echo=FALSE, results='asis', message=FALSE}
db <- read_excel("students.xlsx", "students", na = "NA")
class(db) <- "data.frame"

db_msc <- db[db$grade == "MSc", ]
db_msc <- db_msc[order(db_msc$year, decreasing = TRUE), ]
cat(sprintf("### MSc students (%d)\n", nrow(db_msc)))

for (i in seq(nrow(db_msc)))
  print_student(db_msc[i, ], nrow(db_msc) - i + 1)

db_bsc <- db[db$grade == "BSc", ]
db_bsc <- db_bsc[order(db_bsc$year, decreasing = TRUE), ]
cat(sprintf("### BSc students (%d)\n", nrow(db_bsc)))

for (i in seq(nrow(db_bsc)))
  print_student(db_bsc[i, ], nrow(db_bsc) - i + 1)
```

### Short-term scientific missions (4)

* **Fabian Dupont**, October 2015   
    MSc Medicine, Technische Universität München   
    Health and economic impact of _Taenia solium_ neurocysticercosis in Uganda
    
* **Uffe Christian Braae**, December 2014   
    PhD Veterinary Medicine, University of Copenhagen   
    Development of a _Taenia solium_ transmission model
    
* **Hardy Richter**, September 2014   
    Research associate, Munich Global Neurology Group   
    Landscape analysis of _Taenia solium_ neurocysticercosis in Europe
    
* **Chiara Trevisan**, July 2014   
    PhD Veterinary Medicine, University of Copenhagen   
    Burden assessment of _Taenia solium_ cysticercosis in Tanzania
    
### PhD examination committees (4)

* **Lea Sletting Jakobsen**, November 2017   
    PhD Nutrition, National Food Institute, Danish Technical University   
    Method development in the study of burden of disease of foodborne chemicals  
    Promoters: Morten Poulsen; Sara Monteiro Pires, Maarten Nauta
    
* **Malgorzata Jennes**, October 2017   
    PhD Veterinary Sciences, Ghent University   
    Novel insights in the host-pathogen interaction of porcine toxoplasmosis  
    Promoters: Eric Cox; Pierre Dorny, Stéphane De Craeye  
    
* **Elvire Mfueni Bikundi**, June 2016   
    PhD Public Health, Université catholique de Louvain   
    Mieux comprendre les relations entre les déterminants socioéconomiques, la couverture en moustiquaires et la prévalence du paludisme chez les enfants en R.D Congo et en Afrique  
    Promoters: Niko Speybroeck; Robert Snow  
    
* **Marco Coral Almeida**, February 2016   
    PhD Veterinary Sciences, Ghent University   
    Epidemiological transmission patterns of _Taenia solium_ cysticercosis in endemic areas: The case of Ecuador  
    Promoters: Pierre Dorny; Sarah Gabriël, Emmanuel Nji Abatih, Washington Benitez  
    
## Scientific output

```{r, echo=FALSE, message=FALSE}
db <- read_excel("publications.xlsx", "chapters", na = "NA")
class(db) <- "data.frame"

db <- db[order(db$title), ]
db <- db[order(db$date, decreasing = TRUE), ]
```

```{r, echo=FALSE, results='asis'}
cat(sprintf("### Book chapters (%d)", nrow(db)))
```

```{r, echo=FALSE, results='asis', message=FALSE}
for (i in seq(nrow(db))) print_chapter(db[i, ], nrow(db) - i + 1)
```

```{r, echo=FALSE, message=FALSE}
db <- read_excel("publications.xlsx", "papers", na = "NA")
class(db) <- "data.frame"

db <- db[order(db$title), ]
db <- db[order(db$date, decreasing = TRUE), ]
db <- db[order(!is.na(db$volume)), ]
```

```{r, echo=FALSE, results='asis'}
cat(sprintf("### Peer-reviewed papers (%d)", nrow(db)))
```

**[Google Scholar](https://scholar.google.com/citations?user=AFSxtd0AAAAJ) metrics: `r gs$total_cites` citations &middot; h-index `r gs$h_index` &middot; i10-index `r gs$i10_index`**

```{r, echo=FALSE, results='asis', message=FALSE}
for (i in seq(nrow(db))) print_article(db[i, ], nrow(db) - i + 1)
```

```{r, echo=FALSE, message=FALSE}
db <- read_excel("publications.xlsx", "submitted", na = "NA")
class(db) <- "data.frame"

db <- db[order(db$title), ]
db <- db[order(db$date, decreasing = TRUE), ]
```

```{r, echo=FALSE, results='asis'}
cat(sprintf("### Submitted manuscripts (%d)", nrow(db)))
```

```{r, echo=FALSE, results='asis', message=FALSE}
for (i in seq(nrow(db))) print_article(db[i, ], nrow(db) - i + 1)
```

```{r, echo=FALSE, message=FALSE}
db <- read_excel("presentations.xlsx", "oral", na = "NA")
class(db) <- "data.frame"

db <- db[order(db$title), ]
db <- db[order(db$month, decreasing = TRUE), ]
db <- db[order(db$year, decreasing = TRUE), ]
```

```{r, echo=FALSE, results='asis'}
cat(sprintf("### Oral presentations (%d)", nrow(db)))
```

```{r, echo=FALSE, results='asis', message=FALSE}
for (i in seq(nrow(db))) print_proceeding(db[i, ], nrow(db) - i + 1)
```

```{r, echo=FALSE, message=FALSE}
db <- read_excel("presentations.xlsx", "poster", na = "NA")
class(db) <- "data.frame"

db <- db[order(db$title), ]
db <- db[order(db$month, decreasing = TRUE), ]
db <- db[order(db$year, decreasing = TRUE), ]
```

```{r, echo=FALSE, results='asis'}
cat(sprintf("### Poster presentations (%d)", nrow(db)))
```

```{r, echo=FALSE, results='asis', message=FALSE}
for (i in seq(nrow(db))) print_proceeding(db[i, ], nrow(db) - i + 1)
```

### Reports (13)

* Food and Agriculture Organization of the United Nations, World Health Organization (2019) Attributing illness caused by Shiga toxin-producing _Escherichia coli_ (STEC) to specific foods. JEMRA Microbiological Risk Assessment Series. http://www.fao.org/publications/card/en/c/CA5758EN

* Devos C, Cordon A, Lefèvre M, Obyn C, Renard F, Bouckaert N, Gerkens S, Maertens de Noordhout C, **Devleesschauwer B**, Haelterman M, Léonard C, Meeus P. Performance of the Belgian health system – report 2019. Health Services Research (HSR) Brussels: Belgian Health Care Knowledge Centre (KCE). 2019. KCE Reports 313. D/2019/10.273/34. https://kce.fgov.be/en/performance-of-the-belgian-health-system-%E2%80%93-report-2019

* Renard F, **Devleesschauwer B** (2019) Health Status Report 2019: De gezondheidstoestand in België. Brussels, Belgium: Sciensano; 48p. Report number D/2019/14.440/4. https://doi.org/10.25608/reh4-ty02

* Renard F, **Devleesschauwer B** (2019) Health Status Report 2019: L'état de santé en Belgique. Brussels, Belgium: Sciensano; 48p. Report number D/2019/14.440/3. https://doi.org/10.25608/a42z-ah78

* Federal Agency for the Safety of the Food Chain (2019) The FASFC analyses program regarding process contaminants (dossier SciCom 2018/03). http://www.afsca.be/scientificcommittee/opinions/2019/_documents/Advice02-2019.pdf

* Federal Agency for the Safety of the Food Chain (2018) The analysis program regarding microbiological analyses in prepared products, fish products, vegetables, fruit, herbs, vegetable oil, fertilizers, beverages and water not intended for drinks (dossier SciCom 2017/24). http://www.afsca.be/scientificcommittee/opinions/2018/_documents/Advice15-2018.pdf

* Food and Agriculture Organization of the United Nations, World Health Organization (2018) Shiga toxin-producing _Escherichia coli_ (STEC) and food: attribution, characterization, and monitoring. JEMRA Microbiological Risk Assessment Series. http://www.fao.org/documents/card/en/c/CA0032EN

* Graham H, Martijn Bouwknegt M, **Devleesschauwer B**, Robertson L, van der Giessen L (2016) COST Action FA1408: European ranking of foodborne parasites. Results of a workshop held to prioritise foodborne parasites in Europe using multicriteria decision analyses, 8--12 February 2016, RIVM Bilthoven.

* World Health Organization (2015) WHO estimates of the global burden of foodborne diseases. Foodborne diseases burden epidemiology reference group 2007--2015. Geneva: WHO Press. http://www.who.int/foodsafety/publications/foodborne_disease/fergreport/en/

* Smit S, **Devleesschauwer B**, Apers L, Macq J, Beutels P, Speybroeck N (2015) Evaluation of the cost-effectiveness of the tuberculosis policies in Flanders. Report submitted to the Agency for Care and Health.

* Food and Agriculture Organization of the United Nations, World Health Organization (2014) Risk based examples for control of _Trichinella_ spp. and _Taenia saginata_ in meat. Report of a joint FAO/WHO expert meeting, 22--25 October 2013, WHO Headquarters, Geneva, Switzerland. ftp://ftp.fao.org/codex/meetings/CCFH/ccfh46/Trichinella%20Mtg%20Report%20241014.pdf

* World Health Organization (2014) WHO initiative to estimate the global burden of foodborne diseases: fifth formal meeting of the Foodborne Disease Burden Epidemiology Reference Group (FERG), 8--12 April 2013, Geneva, Switzerland. Geneva: WHO Press. http://www.who.int/foodsafety/publications/ferg5/en/

* World Health Organization (2014) WHO initiative to estimate the global burden of foodborne diseases: fourth formal meeting of the Foodborne Disease Burden Epidemiology Reference Group (FERG): Sharing New Results, Making Future Plans, and Preparing Ground for the Countries. Geneva: WHO Press. http://www.who.int/foodsafety/publications/ferg4/en/

### R Packages

```{r, echo=FALSE, message=FALSE, results='asis'}
db <- read_excel("Rpackages.xlsx", "tab", na = "NA")
class(db) <- "data.frame"

db <- db[order(db$date, decreasing = TRUE), ]
for (i in seq(nrow(db))) {
  print_package(db[i, ], nrow(db) - i + 1)
}
```

### Vulgarizing articles

* _In a tobacco-free world, life expectancy increases by 2 years._ Sciensano news, 11 December 2019. https://www.sciensano.be/en/press-corner/a-tobacco-free-world-life-expectancy-increases-2-years
* _Acute gastroenteritis cost the Belgian economy hundreds of millions euros every year._ Sciensano news, 26 June 2019. https://www.sciensano.be/en/press-corner/acute-gastroenteritis-cost-belgian-economy-hundreds-millions-euros-every-year
* _New! Belgian Health Status Report available online._ Sciensano news, 22 February 2019. https://www.sciensano.be/en/press-corner/new-belgian-health-status-report-available-online
* _Belgium drops from 8th to 15th place on the European ladder of healthy life years._ Sciensano news, 16 July 2018. https://www.sciensano.be/en/press-corner/belgium-drops-8th-15th-place-european-ladder-healthy-life-years
* _One in 10 globally suffer from foodborne diseases, WHO study finds._ EPI News, 3 December 2015. http://news.ufl.edu/articles/2015/12/one-in-10-globally-suffer-from-foodborne-diseases-who-study-finds.php
* _Des nombres pour des aliments sûrs._ La Libre Belgique, 12 April 2015.
* _Comment les nombres rendent vos aliments plus sûrs._ Le Soir, 8 April 2015.
* _Hoe getallen je voedsel veiliger maken._ De Morgen, 7 April 2015. https://www.demorgen.be/opinie/hoe-getallen-je-voedsel-veiliger-maken-b7910eb9/

## Scientific honors and awards

* **Odile Bain Memorial Prize**, Parasites & Vectors; 2018
* **PhD Scholarship**, Special Research Fund (BOF), Ghent University; 2010
* **Pfizer Award** for the best Master thesis in Veterinary Medicine; 2010
* **Dr Paul Janssen Award** for the best Master student in Veterinary Medicine; 2010
* **Floribert Jurion Fund**, Royal Academy for Overseas Sciences; 2009
* **Travel grant**, BIOS, Ghent University; 2008
* **Travel grant**, Flemish Inter-University Council---University Development Cooperation (VLIR-UOS); 2007

---

_Last update: `r Sys.Date()`_